# 이민영 지니 데이터 가져오기 (사랑의콜센타)

```{r}
library(httr)
library(rvest)
library(RSelenium)

remD <- remoteDriver(port = 4445L, browserName = "chrome")
remD$open()



```{r}
### 함수 시작 ()
remD$navigate(paste0("https://www.genie.co.kr/search/searchSong?query=", a))
html <- remD$getPageSource()[[1]]
html <- read_html(html)

title <- NULL
artist <- NULL
number <- NULL


artist <- html %>% html_nodes(".info .artist") %>%
  html_text()
artist <- gsub("\n", "", artist)
artist <- trimws(artist) 

number <- html %>% html_nodes("tbody > tr") %>%
  html_attrs()

for(i in 1:length(number)){
  number[[i]] <- number[[i]][2]
}
number <- gsub("songid", "", number)

df <- data.frame(number, artist)
df

library(dplyr)

genre <- c()
title <- c()
heart <- c()
t.listener <- c()
t.listen <- c()


for(i in df$number){
  url <- paste0("http://www.genie.co.kr/detail/songInfo?xgnm=", i)

  url_n <- read_html(url)
  
  genres_nodes_n <- html_nodes(url_n, 'li>span.value')
  genres_n <- html_text(genres_nodes_n)
  
  genre <- append(genre, genres_n[3])
  
  title_nodes_n <- html_nodes(url_n, '#body-content > div.song-main-infos > div.info-zone > h2')
  title_n <- html_text(title_nodes_n)
  title_n <- gsub("\n", "", title_n)
  title_n <- trimws(title_n)
  title <- append(title, title_n)
  
  heart_nodes_n <- html_nodes(url_n, '#emLikeCount')
  heart_n <- html_text(heart_nodes_n)
  heart <- append(heart, heart_n)
  
  heart_nodes_n <- html_nodes(url_n, '#emLikeCount')
  heart_n <- html_text(heart_nodes_n)
  heart <- append(heart, heart_n)
  
  t.listener_nodes_n <- html_nodes(url_n, '#body-content > div.song-main-infos > div.aside-zone.daily-chart > div.total > div:nth-child(1) > p')
  t.listener_n <- html_text(t.listener_nodes_n)
  t.listener <- append(t.listener, t.listener_n) 
  
  t.listen_nodes_n <- html_nodes(url_n, '#body-content > div.song-main-infos > div.aside-zone.daily-chart > div.total > div:nth-child(2) > p')
  t.listen_n <- html_text(t.listen_nodes_n)
  t.listen <- append(t.listen, t.listen_n)
  

}
df <- data.frame(df, title, genre, heart, t.listener, t.listen)
return(df)
### 함수 끝

```

```{r}
love_call_center <- 함수이름("사랑의콜센타")

```